Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-16 blind.tex
Sync with local to fix smart quotes

To resolve the issue, we let the verifier to switch to a fresh new key for each round of the protocol. For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$. Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoid the issue of circuit privacy. Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$. This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$. By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol.

@@

Here we present our compiler on $\QPIP_0$ protocols that can be used to achieves blindness.
The high level idea is to run the protocol under homomorphic encryption.
A classical version of this compiler appears in \cite{KMThesis}, where it is used to make protocols computationally simulatable.
We have a classical client and a quantum server.
So we choose the quantum homomorphic encryption from \cite{mahadev_qfhe} that's compatible with classical clients.
More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
Furthermore, we notice that the ciphertexts can be split into registers as with the corresponding plaintext.

A naive approach is to encrypt the initial input,
run the entire protocol homomorphically,
then decode the output at the very end.
However, it is difficult to prove the soundness this way because homomorphic encryption schemes doesn't guarantee circuit privacy;
the server could learn about ther client's coins.
Furthermore, the prover would also be allowed to send invalid ciphertexts...?
\Ethan{Can't we assume all ciphertexts are valid, and ``invalid" ones just decodes to $\bot$?}
So instead we let the verifier decrypt every round.
Then, in order the preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
Which results in the following protocol.

@@

%\Ethan{General comment: Make story more interesting. Clearly claim our own contributions.}

\KM{notation inconsistency...}

We proceeds to present our compiler. We start by introducing the notation of a $\QPIP_0$ protocol $\Pi$ as follows.
% We now state our compiler that gives any $\QPIP_0$ protocol blindness.

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
	Inputs:
	\begin{itemize}
		\item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Verifier's input: $x\in\zo^n$
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $L$ be the maximum circuit depth of $\cP_t$.
	\end{itemize}

@@

	For all $t$, from the perspective of the prover,
	as it receives no information on $sk_t$,
	$\Hyb_{t+1}^x$ is computationally indistinguishable from $\Hyb_t^x$ due to the CPA security of $\QHE$ under $pk_t$.
	By a standard hybrid argument, we observe that $\Hyb_1^x$ is computationally indistinguishable with $\Hyb_{T+1}^x$.
	We use the the same argument for the computational indistinguishability between $\Hyb_1^0$ and $\Hyb_{T+1}^0$.
	We conclude that $P^*$ cannot distinguish between $\Hyb_{T+1}^x$ and $\Hyb_{T+1}^0$,
	therefore $\Piblind$ is blind.
\end{proof}

@@

%Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19},
%as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.

>>>>

To resolve the issue, we let the verifier switch to a fresh new key for each round of the protocol. For example, when the prover $\Pblind$ returns the ciphertext of his first message, the verifier $\Vblind$ decrypts the ciphertext \Ethan{Need to mention somewhere that if $\QDec$ fails, it outputs $\bot$ instead of aborting}, computes his next message (in the clear), and then encrypt it using a fresh key $pk'$ and sends it to $\Pblind$. Since the verifier $\Vblind$ only  sends fresh ciphertexts to $\Pblind$, this avoids the issue of circuit privacy. Additionally, to allow $\Pblind$ to homomorphically evaluate its next message, $\Vblind$ needs to encrypt the previous secret key $sk$ under the new public key $pk'$ and send it to $\Pblind$. This allows the prover to homomorphically convert ciphertexts under key $pk$ to ciphertexts under key $pk'$. By doing so, we show that for any cheating prover $\Pblindstar$, the interaction $(\Pblindstar, \Vblind)$ indeed simulates a valid interaction of $(\Pstar, V)$ for some cheating $\Pstar$, and hence the soundness of $\Pi$ implies the soundness of the compiled protocol. Finally, for the issue of the prover sending invalid ciphertext, we can assume without loss of generality that the decryption

@@

Here we present our compiler on $\QPIP_0$ protocols that can be used to achieve blindness.
The high level idea is to run the protocol under homomorphic encryption.
A classical version of this compiler appears in \cite{KMThesis}, where it is used to make protocols computationally simulatable.
We have a classical client and a quantum server.
So we choose the quantum homomorphic encryption from \cite{mahadev_qfhe} that's compatible with classical clients.
More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
Furthermore, we notice that the ciphertexts can be split into registers as with the corresponding plaintext.

A naive approach is to encrypt the initial input,
run the entire protocol homomorphically,
then decode the output at the very end.
However, it is difficult to prove the soundness this way because homomorphic encryption schemes doesn't guarantee circuit privacy;
the server could learn about its client's coins.
Furthermore, the prover would also be allowed to send invalid ciphertexts...?
\Ethan{Can't we assume all ciphertexts are valid, and ``invalid" ones just decodes to $\bot$?}
So instead we let the verifier decrypt every round.
Then, in order to preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
Which results in the following protocol.

@@

%\Ethan{General comment: Make the story more interesting. Clearly claim our own contributions.}

We proceed to present our compiler. We start by introducing the notation of a $\QPIP_0$ protocol $\Pi$ as follows.
% We now state our compiler that gives any $\QPIP_0$ protocol blindness.

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ corresponding to $\Pi_0$}
    Inputs:
    \begin{itemize}
        \item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$
        \item Verifier's input: $x\in\zo^n$
    \end{itemize}

    Ingredients:
    \begin{itemize}
        \item Let $L$ be the maximum circuit depth of $\cP_t$.
    \end{itemize}

@@

    For all $t$, from the perspective of the prover,
    as it receives no information on $sk_t$,
    $\Hyb_{t+1}^x$ is computationally indistinguishable from $\Hyb_t^x$ due to the CPA security of $\QHE$ under $pk_t$.
    By a standard hybrid argument, we observe that $\Hyb_1^x$ is computationally indistinguishable with $\Hyb_{T+1}^x$.
    We use the same argument for the computational indistinguishability between $\Hyb_1^0$ and $\Hyb_{T+1}^0$.
    We conclude that $P^*$ cannot distinguish between $\Hyb_{T+1}^x$ and $\Hyb_{T+1}^0$,
    therefore $\Piblind$ is blind.
\end{proof}

@@

%Our compiler is a straightforward way of achieving blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
%In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{arXiv:ChiaChungYam19, arXiv:AlaChiHun19},
%as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.
